---
title: "Imputation using mice"
output: html_document
---
# reading the data and structure of the data. counting the percentage of na values available in the data in each variable.
```{r}
#library(naniar)
HRTrain_featureanalysis <- read.csv(file = "HRTrainData.csv", sep = ",", na.strings = "")
str(HRTrain_featureanalysis)
p <-function(x){sum(is.na(x))/length(x)}*100
apply(HRTrain_featureanalysis,2,p)
```


# using mice library to deal with missing data

```{r}
library(mice)
md.pattern(HRTrain_featureanalysis)
```
# so in the above we are getting 2409 na values or missing values in the education variable and 4124 na/missing values in the previous year rating
# doing the variable pair wise analysis of the data.


```{r}
md.pairs(HRTrain_featureanalysis)
```
# doing the imputation of the missing data

```{r}
impute<- mice(HRTrain_featureanalysis[,2:14], m= 3, seed = 123)
```
```{r}
print(impute)
```


### so imputation has replaced the na values in education using the polyreg which is Bayesian Polytomous Regression as the education has fator variables more than 2 and use Predictive Mean Matching(PMM) for previous year rating.


### printing the imputed values for the previous year rating


```{r}
impute$imp$previous_year_rating
```

### Here we get the 3 imputations for both the variables. This is for the previous year rating and for education will be shown later.
### In this 3 imputation for the previous year rating which one seems best fit will go for that imputation by doing some random analysis of the missing value variables.


## Imputation for the education variable

```{r}
impute$imp$education
```


### Now to complete the data with the imputated values for which I have consisdered the 1st column of the imputation


```{r}
newdataHR<-complete(impute,1)
head(newdataHR)
```

